Clustering galaxies at 0.5 < $z$ < 1: an unsupervised approach

### 2016-05-13 sections0.02/results0.02.tex
Draft 0.02

    %%% should I move this paragraph to method section?!
    In order to find sufficient size for the trained networks, we created maps with sizes from $1\times2$ to $50\times50$.
    Varying grid of the maps helps us to monitor whether grouping galaxies in smaller maps is based on their similar SEDs or its for the shortage of the neurons.
    Based on size the data and SOM results, we chose maximum of the grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
    For each grid we created different SOMs with different learning factors, neighbourhood distances, and iteration numbers to find the optimum result for our sample.
    We created the final SOMs with following initial values: number of iterations in ordering phase = 1000; ordering phase learning factor = 0.9; tuning phase learning factor= 0.02; and tuning phase neighbourhood distance to be 1.

@@

    For each generated network, we compared the results with K96 categorization.
    We also used these networks to classify the T12 galaxies samples, and compared them with classifications from supervised networks in T12.
    \subsection{1D SOMs}
    \label{sec: 1D}
        \subsubsection{TRAINING THE NETWORKS}
        \label{sec: 1Dt}
            To start our clustering, we assumed that galaxies can be divided only in two types; quiescent and star burst.
            In this case, we generated a network with only two neurons.
            We increased the size of the map gradually till we separated the input 12 sample galaxies into the 12 neurons.

            Figs.~\ref{fig: 1by2T} -~\ref{fig: 1by22T} show results of training networks.
            Similar to Fig.~\ref{fig: sample}, the upper part of the figures shows neurons and their relative distances ($D_j$) from each other.
            As it was mentioned in the Sec.~\ref{sec: method}, the colours between neurons represents the relative distance, $D_j$, between the neurons and the darker is the colour the more $D_j$ is between them.
            The lower part shows how many galaxies from K96 template places in each neuron. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_2.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_2.png}
                \end{subfigure}
                \caption{Results of training network in $1\times2$~grid. Similar to Fig.~\ref{fig: sample} the upper plot is a distance map and the lower plot is a hit map. In this network, 5 of galaxies from K96 model, categorized as quiescent galaxies and the rest are star bursts. Because of their high emission lines, Sc galaxies moved towards the star burst ones.}
                 \label{fig: 1by2T}
            \end{figure}

            In the upper map in Fig.~\ref{fig: 1by2T}, the dark colour between two neurons indicates that the $D_j$ between these two groups are relatively high, and these two groups are distinguishable groups. 
            In the lower part of Fig.~\ref{fig: 1by2T}, we see galaxies divided to two groups of 5 and 7.
            Although we know from K96 and T12 that 6 of the galaxies are quiescent and the other 6 are star bursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
            In this method, the Sc galaxies have been categorized as star burst galaxy due to the relatively higher amount of the disk stellar population relative to the bulge ones. 
            According to K96, Sc galaxies are considered as late Hubble type galaxies which have more flat SED compare to other quiescent galaxies.

            Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
            In these plots we forced the galaxies to categorize themselves in maximum 3 groups. 
            If the galaxies in Fig.~\ref{fig: 1by2T} were very similar to each other or were exactly the same, they still wanted to be divided into two groups and left the middle node empty. 
            However, in the lower part of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two galaxies.
            These two galaxies, which are separated from group of star burst galaxies in the lower part of Fig.~\ref{fig: 1by2T}, belong to SB5 and SB6 types.
            In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
            The black colour indicates that the left neuron is completely different from the other two groups.
            While the white colour shows the two neurons are very similar to one another.

            Comparing Fig.~\ref{fig: 1by2T} with Fig.~\ref{fig: 1by3T} shows us that the star burst galaxies are divided into two groups. 
            Based on the colours between these two groups, we conclude that they are very similar groups; both groups are star burst galaxies and have strong emission lines.
            However, SB5 and SB6 types have the most internal extinctions.
            The high amount of extinction causes SED become more flat in the lower wavelength regions.
            The flatness in the UV part of the SED eventually makes these two types of galaxies become more similar to quiescent galaxies than other star burst ones.
            So in the networks, SB5 and SB6 types intend to move more towards the early type galaxies.

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_3.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_3.png}
                \end{subfigure}
                \caption{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times3$~grid. In this network again, 5 of galaxies from K96 model, categorized as quiescent galaxies, and 7 as star bursts. However, this time 2 of galaxies (SB5, and SB6) are separated star bursts groups.}
                 \label{fig: 1by3T}
            \end{figure}

            We increased the size of maps gradually till the galaxies were divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
            Since there are more nodes in higher grid SOMs, the program pays more attention to small differences between each group.
            Higher the size of the maps means that even considering the smallest differences between galaxies.
            If the galaxies from K96 had completely different and distinct SED, SOM with size of $1\times12$ were expected to show 12 different groups of galaxies (1 at each node).
            However, in Fig.~\ref{fig: 1by12T}, we see that three of neurons contains two galaxies and  three of them are empty. 
            In Fig.~\ref{fig: 1by12T} from left to right galaxies with types of B and E, SB3 and SB4, and SB1 and SB2, are the ones groups together. 
            The SB3 and SB4 grouping breaks when we increased the size of the network to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 galaxies remained in the same neurons till we increased the size of map to $1\times20$~(Fig.~\ref{fig: 1by20T}), and the separation between galaxies B and E had not happened before the size of the SOM reached to $1\times22$~(Fig.~\ref{fig: 1by22T}).
        \begin{figure*}
            \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_22.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_22.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
            \end{subfigure}
            \caption{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
            \label{fig: 1by22T}
        \end{figure*} %PB160427: this figure looks really great! Very easy to understand.

            In Fig.~\ref{fig: 1by22T}, in lower plot we can see twelve different groups. 
            In upper plot 5 groups are in the left side neurons, and there are two dark grey colours between them and then the rest of the galaxies. 
            It shows that although we separated the galaxies in twelve groups, but they are still divided in two main groups.
            The closest occupied neurons in the star burst side of the SOM, belongs to the SB6 type. 
            This type of the galaxies has the most extinction and its SED has similarity to early type galaxies more than other star burst types.

            The fact that the galaxies had to have 22 different neurons till be divided into 12 groups, shows that the difference between SB1 and SB2, and B and E galaxies are very small.
            These small differences might be very small.
            Therefore, they intend to stay in the same group till the network become big enough to make attention to the smallest particularity.
           % For using SOM method, one should be careful about these small differences and consider that how much details do we need to pay attention to, to consider two groups are separate from each other.
           %%%% (I'm not sure if it is good to be here or not)
        \subsubsection{ CLASSIFYING SAMPLE OF GALAXIES}
         \label{sec: 1Dv}
            We used each network that we trained in Sec.~\ref{sec: 1Dt}, to classifying the sample 142 galaxies from T12.
            Upper plot in Fig.~\ref{fig: 1by2V} shows the result of the classifying of the T12 galaxies using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
            It shows that 80 of the galaxies have SEDs similar to the early type galaxies and the SEDs of the rest of them are similar to star burst galaxies.
            The lower plot shows the average SED of the galaxies in each node. 
            The left plot shows the average SED of 80 galaxies that classify as an early type galaxies. 
            These galaxies are similar to the ones in the left node in the upper plot in Fig.~\ref{fig: 1by2T}.
            The plots clearly show the 4000\AA~break in the SEDs, which is one of the signatures of the early type galaxies.
            The strong emission lines in that figure could be from the galaxies with similar SED to Sa galaxies but with more strong emission lines.
            The right plot in the lower part of Fig.~\ref{fig: 1by2V} shows strong emission lines and high emissions in the lower wavelengths, which are the signs of the strong star formation in the galaxies. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classifying galaxies from T12, based on their SEDs using $1\times2$~networks that were trained from 12 galaxies in Fig.~\ref{fig: 1by2T}. Up: the same as other hit maps, numbers in each node represents the number of galaxies that belong to that group. In this case 80 means that 80 of the 142 galaxies classify as the early type groups while the 62 of the 142 galaxies categorize to the star burst galaxies. Down: Average SED of the SEDs of the galaxies in each group. The left plot shows the average SED of the 80 galaxies (early type ones), and the right plot shows the average SED of the SEDs of 62 galaxies (the star burst ones).}
                \label{fig: 1by2V}
            \end{figure}            
            Since in this network galaxies forced to be divided into maximum two groups, for any SED between these two groups the SOM must decide that each galaxy belongs to which group based on strongest features of its SED.
            The galaxies with a weak 4000\AA~break but strong emission lines and increase of the flux in the lower wavelengths categorized as star bursts while galaxies with strong 4000\AA~break, but high emission lines categorized as the early type.
            Increasing the size of the SOM helps to solve the problem of the galaxies which have features of both groups.

             Fig.~\ref{fig: 1by3V} represents the result of the classifying the SED of the galaxies using the $1\times3$~network (from Fig.~\ref{fig: 1by2T}). 
             In the upper plot of this figure we can see 66 of the galaxies belongs to the early type group, and 47 belong to star burst galaxies. 
             29 of the galaxies are more similar to star burst ones, but not with all of their features. 
             These groups of galaxies have strong emission lines and the ascending slope towards the lower wavelengths, but they also have a strong 4000\AA~break, which makes them to move towards the early type galaxies (middle plot in the lower part of Fig.~\ref{fig: 1by2V}).

@@

            In Fig.~\ref{fig: 1by22V}, we used the $1\times22$~network to classify the sample galaxies.
            As mentioned in the Sec.~\ref{sec: 1Dt}, this network size is the first size that we could see the K96 galaxies separated in 12 different neurons.
            B and E or SB1 and SB2 galaxies were too similar to SOM can recognize them as two separate groups.
            The same as Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, upper plot of Fig.~\ref{fig: 1by22V} shows how many of galaxies from the 142 galaxies, moved to each neuron in the $1\times22$ SOM.
            \begin{figure*}
                \begin{subfigure}[b]{0.9\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_22_n.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.9\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by22.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times22$ (Fig.~\ref{fig: 1by22T}) to classify the sample galaxies. In the average SED of each neuron, we can clearly see the changes from early type galaxies in the star burst ones. 4000\AA~ break reduces from left to right and emission lines increase.}
                \label{fig: 1by22V}
            \end{figure*}
            The lower plot of the figure represents the average SED of the galaxies in each neuron.
            However, this time, since galaxies had more space to separate some of the neurons left empty. 
            Thus, instead of having 22 average SED plots in the lower part of Fig.~\ref{fig: 1by22V}, we have 12 SEDs.

@@

            In the first two neurons of the upper plot in Fig.~\ref{fig: 1by22V}, there is no galaxy, while in galaxies B and E are in the same neurons in the trained network.
            So we can conclude that there is no galaxy with similar specification of type B or E in the T12 sample.
            There are 3 galaxies in the third neuron, which shows these 3 galaxies are very much similar to the S0 type. 
            18 of the galaxies are on the fifth neurons and similar to the Sa type of the galaxies, while the 7 galaxies in the fourth neurons have SEDs similar to both S0 and Sa galaxies.
            There is one Sb type galaxy and 15 galaxies with SED similar to both Sa and Sb type galaxies.
            The following two neurons (eighth and ninth neurons from the left) are on the edge of the early type and star burst galaxies.
            In the upper plot in the  Fig.~\ref{fig: 1by22T}, the colour between these two neurons are black, which indicates that the weights between these two are really different from each other.
            Therefore, 24 galaxies in the eighth neurons have similar SEDs to Sb type galaxies and SEDs of the 14 galaxies in the ninth neurons are similar to the SB6 galaxies.
            The far right of the network, galaxies with SED comparable to type SB1 and SB2.

@@

        \begin{figure*}
            \centering
            \includegraphics[width=\textwidth]{../images0.01/1d/props5.png}
            \caption{Comparing the median of four propertied of galaxies in each nod in $1\times2$, $1\times4$, and $1\times8$ networks.}
            \label{fig: props}
        \end{figure*}

        Fig.~\ref{fig: props} shows the results of the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in $1\times2$, $1\times4$, and $1\times8$ networks.
        In all the plots $x$-axis shows the number of the neurons divided by the size of the network, and $y$-axis shows one of the mentioned properties.

        In Fig.~\ref{fig: props}, from early type galaxies to star burst ones, stellar mass and age decreases while sSFR and $f_\mathrm{burst}$ increases, in all three lines. 
        These trends are another evidence that this method is working and can be used to categorize galaxies based on their SEDs or even their physical properties.

        N09 used various models to derive galaxies' properties.
        Through these models, some of the properties are already known to be correlated with each others, i.e. stellar mass and star formation rate.
        They, however, studied other relations between properties of a sample of SINGS galaxies which didn't have a direct correlation in the models.
        They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggested that younger stellar population correlate with high SFR.
        They also found the correlation between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
        Since in {\em CIGALE} code, stellar mass is a free parameter, N09 argued that any stellar mass related correlation must be astrophysically meaningful. 
        They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
        T12 replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than N09 results.

               \begin{figure*}
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{../images0.01/1d/f1.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{../images0.01/1d/f2.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{../images0.01/1d/f3.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{../images0.01/1d/f4.png}
        \end{subfigure}
        \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{../images0.01/1d/f5.png}
        \end{subfigure}
       \hfill
        \begin{subfigure}[b]{0.3\textwidth}
            \includegraphics[width=\textwidth]{../images0.01/1d/f6.png}
        \end{subfigure}
        \caption{From up to down: Correlation between age (t$_{\rm {D4000}}$) and sSFR ($\phi$), sSFR and stellar mass, age (t$_{\rm {D4000}}$) and stellar mass, and A$_{\rm {FUV}}$ with sSFR, age (t$_{\rm {D4000}}$) and stellar mass. Points show the mean values of these properties of galaxies in $1\times22$ network and error bars are the standard deviation of the mean values. colours shows the type of the galaxies in the new classification. The most pure red colour shows E type galaxies and the most blue one indicates the SB1 galaxies. The other colours depend on how much they are close to red or blue show that the galaxies are early type or star burst.}
        \label{fig: props_vs_props}
    \end{figure*}

>>>>

    In order to find sufficient size for the trained networks, we created maps with sizes from $1\times2$ to $50\times50$.
    Varying grid of the maps helps us to monitor whether grouping galaxies in smaller maps is based on their similar SEDs or its for the shortage of the neurons.
    Based on size the data and SOM results, we chose maximum of the grid size to be $1\times22$ and $12\times12$ in 1D and 2D maps, respectively. 
    For each grid we created different SOMs with different learning factors, neighbourhood distances, and iteration numbers to find the optimum result for our sample.
    We created the final SOMs with following initial values: number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance to be 1000, 0.9, 0.02, and 1, respectively.

@@

    For each generated network, we compared the results with K96 categorization.
    We also used these networks to classify the T12 galaxies samples, and compared them with classifications from supervised networks in T12.
    \subsection{1D SOMs}
    \label{sec: 1D}
        \subsubsection{TRAINING THE NETWORKS}
        \label{sec: 1Dt}
            To start our clustering, we assumed that galaxies can be divided only in two types; quiescent and starburst.
            In this case, we generated a network with only two neurons.
            We increased the size of the map gradually till we separated the input 12 sample galaxies into the 12 neurons.

            Figs.~\ref{fig: 1by2T} -~\ref{fig: 1by22T} show results of training networks.
            Similar to Fig.~\ref{fig: sample}, the upper part of the figures shows neurons and their relative distances, $D_j$, from each other.
            As it was mentioned in the Sec.~\ref{sec: method}, the colours between neurons represents the relative distance between the neurons and the darker is the colour the more relative distance is between them.
            The lower part shows how many galaxies from K96 template places in each neuron. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_2.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_2.png}
                \end{subfigure}
                \caption{Results of training network in $1\times2$~grid. Similar to Fig.~\ref{fig: sample} the upper plot is a distance map and the lower plot is a hit map. In this network, 5 of galaxies from K96 model, categorized as quiescent galaxies and the rest are starbursts. Because of their high emission lines, Sc galaxies moved towards the starburst ones.}
                 \label{fig: 1by2T}
            \end{figure}

            In the upper map in Fig.~\ref{fig: 1by2T}, the dark colour between two neurons indicates that the relative distance between these two groups are relatively high, and these two groups are distinguishable groups.
            In the lower part of Fig.~\ref{fig: 1by2T}, we see galaxies divided to two groups of 5 and 7.
            Although we know from K96 and T12 that 6 of the galaxies are quiescent and the other 6 are starbursts, the SOM results show 5 of the galaxies in one group and the other 7 in the second group.
            In this method, the Sc galaxies have been categorized as starburst galaxy due to the relatively higher amount of the disk stellar population relative to the bulge ones. 
            According to K96, Sc galaxies are considered as late Hubble type galaxies which have more flat SED compare to other quiescent galaxies.

            Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
            In these plots we forced the galaxies to categorize themselves in maximum 3 groups. 
            If the galaxies in Fig.~\ref{fig: 1by2T} were very similar to each other or were exactly the same, they still wanted to be divided into two groups and left the middle node empty. 
            However, in the lower part of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two galaxies.
            These two galaxies, which are separated from group of starburst galaxies in the lower part of Fig.~\ref{fig: 1by2T}, belong to SB5 and SB6 types.
            In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
            The black colour indicates that the left neuron is completely different from the other two groups.
            While the white colour shows the two right neurons are very similar to one another.

            Comparing Fig.~\ref{fig: 1by2T} with Fig.~\ref{fig: 1by3T} shows us that the starburst galaxies are divided into two groups. 
            Based on the colours between these two groups, we conclude that they are very similar groups; both groups are starburst galaxies and have strong emission lines.
            However, SB5 and SB6 types have the most internal extinctions.
            The high amount of extinction causes SED become more flat at shorter wavelength regions.
            The flatness in the UV part of the SED eventually makes these two types of galaxies become more similar to quiescent galaxies than other starburst ones.
            So in the networks, SB5 and SB6 types intend to move more towards the early type galaxies.

            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_3.png}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_3.png}
                \end{subfigure}
                \caption{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times3$~grid. In this network again, 5 of galaxies from K96 model, categorized as quiescent galaxies, and 7 as starbursts. However, this time 2 of galaxies (SB5, and SB6) are separated starbursts groups.}
                 \label{fig: 1by3T}
            \end{figure}

            We increased the size of maps gradually till the galaxies were divided into twelve groups (Figs.~\ref{fig: 1by4T} to ~\ref{fig: 1by20T} and ~\ref{fig: 1by22T}).
            Since there are more nodes in higher grid SOMs, the program pays more attention to small differences between each group.
            Higher the size of the maps means that even considering the smallest differences between galaxies.
            If the galaxies from K96 had completely different and distinct SED, SOM with size of $1\times12$ were expected to show 12 different groups of galaxies (1 at each node).
            However, in Fig.~\ref{fig: 1by12T}, we see that three of neurons contains two galaxies and three of them are empty, which shows there were no galaxy in K96 sample that can fill those neurons.
            In Fig.~\ref{fig: 1by12T} from left to right galaxies with types of B and E, SB3 and SB4, and SB1 and SB2, are the ones groups together. 
            The SB3 and SB4 grouping breaks when we increased the size of the network to $1\times15$~(Fig.~\ref{fig: 1by15T}).
            The SB1 and SB2 galaxies remained in the same neurons till we increased the size of map to $1\times20$~(Fig.~\ref{fig: 1by20T}), and the separation between galaxies B and E had not happened before the size of the SOM reached to $1\times22$~(Fig.~\ref{fig: 1by22T}).
        \begin{figure*}
            \begin{subfigure}[b]{\textwidth}
                \centering
                \includegraphics[width=\textwidth]{../images0.01/1d/dist_1_by_22.png}
            %\caption{$1\times22$ weight map}
             %\label{fig: 1by22T}
            \end{subfigure}
            \hfill
            \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{../images0.01/1d/hit_t_1_by_22.png}
             %\caption{$1\times22$ hits map}
             %\label{fig: 1by22Thits}
            \end{subfigure}
            \caption{The same as Fig.~\ref{fig: 1by2T} but this time the figure shows results of training network in $1\times22$~grid.}
            \label{fig: 1by22T}
        \end{figure*} %PB160427: this figure looks really great! Very easy to understand.

            In Fig.~\ref{fig: 1by22T}, in lower plot we can see twelve different groups. 
            In upper plot 5 groups are in the left side neurons, and there are two dark grey colours between them and then the rest of the galaxies. 
            It shows that although we separated the galaxies in twelve groups, but they are still divided in two main groups.
            The closest occupied neurons in the starburst side of the SOM, belongs to the SB6 type. 
            This type of the galaxies has the most extinction and its SED has similarity to early type galaxies more than other starburst types.

            The fact that the galaxies had to have 22 different neurons till be divided into 12 groups, shows that the difference between SB1 and SB2, and B and E galaxies are very small.
            These small differences might be very small.
            Therefore, they intend to stay in the same group till the network become big enough to make attention to the smallest particularity.

        \subsubsection{ CLASSIFYING SAMPLE OF GALAXIES}
         \label{sec: 1Dv}
            We used each network that we trained in Sec.~\ref{sec: 1Dt}, to classifying the sample 142 galaxies from T12.
            Upper plot in Fig.~\ref{fig: 1by2V} shows the result of the classifying of the T12 galaxies using the $1\times2$~network from Fig.~\ref{fig: 1by2T}.
            It shows that 80 of the galaxies have SEDs similar to the early type galaxies and the SEDs of the rest of them are similar to starburst galaxies.
            The lower plot shows the average SED of the galaxies in each node. 
            The left plot shows the average SED of 80 galaxies that classify as an early type galaxies. 
            These galaxies are similar to the ones in the left node in the upper plot in Fig.~\ref{fig: 1by2T}.
            The plots clearly show the 4000\AA~break in the SEDs, which is one of the signatures of the early type galaxies.
            The strong emission lines in that figure could be from the galaxies with similar SED to Sa galaxies but with more strong emission lines.
            The right plot in the lower part of Fig.~\ref{fig: 1by2V} shows strong emission lines and high emissions in the lower wavelengths, which are the signs of the strong star formation in the galaxies. 
            \begin{figure}
                \begin{subfigure}[b]{0.5\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_2.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.5\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by2.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Classifying galaxies from T12, based on their SEDs using $1\times2$~networks that were trained from 12 galaxies in Fig.~\ref{fig: 1by2T}. Up: the same as other hit maps, numbers in each node represents the number of galaxies that belong to that group. In this case 80 means that 80 of the 142 galaxies classify as the early type groups while the 62 of the 142 galaxies categorize to the starburst galaxies. Down: Average SED of the SEDs of the galaxies in each group. The left plot shows the average SED of the 80 galaxies (early type ones), and the right plot shows the average SED of the SEDs of 62 galaxies (the starburst ones).}
                \label{fig: 1by2V}
            \end{figure}            
            Since in this network galaxies forced to be divided into maximum two groups, for any SED between these two groups the SOM must decide that each galaxy belongs to which group based on strongest features of its SED.
            The galaxies with a weak 4000\AA~break but strong emission lines and increase of the flux in the lower wavelengths categorized as starbursts while galaxies with strong 4000\AA~break, but high emission lines categorized as the early type.
            Increasing the size of the SOM helps to solve the problem of the galaxies which have features of both groups.

             Fig.~\ref{fig: 1by3V} represents the result of the classifying the SED of the galaxies using the $1\times3$~network (from Fig.~\ref{fig: 1by2T}). 
             In the upper plot of this figure we can see 66 of the galaxies belongs to the early type group, and 47 belong to starburst galaxies. 
             29 of the galaxies are more similar to starburst ones, but not with all of their features. 
             These groups of galaxies have strong emission lines and rising flux towards the ultraviolet, but they also have a strong 4000\AA~break, which makes them to move towards the early type galaxies (middle plot in the lower part of Fig.~\ref{fig: 1by2V}).

@@

            In Fig.~\ref{fig: 1by22V}, we used the $1\times22$~network to classify the sample galaxies.
            As mentioned in the Sec.~\ref{sec: 1Dt}, this network size is the first size that we could see the K96 galaxies separated in 12 different neurons.
            B and E or SB1 and SB2 galaxies were too similar to SOM can recognize them as two separate groups.
            The same as Figs.~\ref{fig: 1by2V} and ~\ref{fig: 1by3V}, upper plot of Fig.~\ref{fig: 1by22V} shows how many of galaxies from the 142 galaxies, moved to each neuron in the $1\times22$ SOM.
            \begin{figure*}
                \begin{subfigure}[b]{0.9\textwidth}
                    \centering
                    \includegraphics[width=\textwidth]{../images0.01/1d/hit_v_1_by_22_n.png}
                    %\caption{$1\times2$ weight map}
                     %\label{fig: 1by3T}
                \end{subfigure}
                \hfill
                \begin{subfigure}[b]{0.9\textwidth}
                     \includegraphics[width=\textwidth]{../images0.01/1d/SED_total1by22.png}
                     %\caption{$1\times2$ hits map}
                     %\label{fig: 1by3Thits}
                \end{subfigure}
                \caption{Same as Fig.~\ref{fig: 1by2V}, but in this figure, we used a network with size of $1\times22$ (Fig.~\ref{fig: 1by22T}) to classify the sample galaxies. In the average SED of each neuron, we can clearly see the changes from early type galaxies in the starburst ones. 4000\AA~ break reduces from left to right and emission lines increase.}
                \label{fig: 1by22V}
            \end{figure*}
            The lower plot of the figure represents the average SED of the galaxies in each neuron.
            However, this time, since galaxies had more space to separate some of the neurons left empty. 
            Thus, instead of having 22 average SED plots in the lower part of Fig.~\ref{fig: 1by22V}, we have 12 SEDs.

@@

            In the first two neurons of the upper plot in Fig.~\ref{fig: 1by22V}, there is no galaxy, while in galaxies B and E are in the same neurons in the trained network.
            So we can conclude that there is no galaxy with similar specification of type B or E in the T12 sample.
            There are 3 galaxies in the third neuron, which shows these 3 galaxies are very much similar to the S0 type. 
            18 of the galaxies are on the fifth neurons and similar to the Sa type of the galaxies, while the 7 galaxies in the fourth neurons have SEDs similar to both S0 and Sa galaxies.
            There is one Sb type galaxy and 15 galaxies with SED similar to both Sa and Sb type galaxies.
            The following two neurons (eighth and ninth neurons from the left) are on the edge of the early type and starburst galaxies.
            In the upper plot in the  Fig.~\ref{fig: 1by22T}, the colour between these two neurons are black, which indicates that the weights between these two are really different from each other.
            Therefore, 24 galaxies in the eighth neurons have similar SEDs to Sb type galaxies and SEDs of the 14 galaxies in the ninth neurons are similar to the SB6 galaxies.
            The far right of the network, galaxies with SED comparable to type SB1 and SB2.

@@

        \begin{figure}
            \centering
            \includegraphics[width=0.5\textwidth]{../images0.01/1d/props5.png}
            \caption{Comparing the median of four propertied of galaxies in each nod in $1\times2$ (balck circles), $1\times4$ (blue diamond), and $1\times8$ (red triangles) networks.}
            \label{fig: props}
        \end{figure}

        Fig.~\ref{fig: props} shows the results of the median of stellar mass, age, specific star formation rate (sSFR; star formation rate per stellar mass), and $f_\mathrm{burst}$ of the galaxies in each neuron in $1\times2$, $1\times4$, and $1\times8$ networks.
        In all the plots horizontal axis shows the number of the neurons divided by the size of the network, and vertical axis shows one of the mentioned properties.

        In Fig.~\ref{fig: props}, from early type galaxies to starburst ones, stellar mass and age decreases while sSFR and $f_\mathrm{burst}$ increases, in all three lines. 
       % These trends are another evidence that this method is working and can be used to categorize galaxies based on their SEDs or even their physical properties. %PB20160510: I would say something more like "the SED categories represent a continuum of physical properties". Of course the physical properties were derived from the SEDs, so maybe this isn't so surprising and you could mention that as well.
        %%%SR20160611: Sorry I am not sure that I understand this comment?
        Considering results from Fig.~\ref{fig: props}, we can clearly see that separating galaxies based on SED types also leads to a separation in properties derived (via {\em CIGALE}) from the SEDs.

        N09 used various models to derive galaxies' properties.
        Through these models, some of the properties are already known to be correlated with each others, i.e. stellar mass and star formation rate.
        They, however, studied other relations between properties, that didn't have any direct correlation in the models, in a sample of SINGS galaxies. %%eHMM I will change the previous sentence! It doesn't read well
        They found a tight correlation between sSFR and t$_{\rm {D4000}}$, which suggested that younger stellar population correlate with high SFR.
        They also found the correlation between stellar mass and SFR, and stellar mass and t$_{\rm {D4000}}$.
        Since in {\em CIGALE} code, stellar mass is a free parameter, N09 argued that any stellar mass related correlation must be astrophysically meaningful. 
        They also studied relations between the attenuation at 1500 \AA~(A$_{\rm {FUV}}$) and sSFR, age, and stellar mass and did not find any correlation.
        T12 replicated the upper plots in Fig.~\ref{fig: props_vs_props}, and found a tighter correlation than N09 results.
